---
title: "ADA Panel Data Confidentialisation"
author: " Project: [Project name]  \nDepositor: [firstname lastname]  \nArchivist:[firstname lastname]  \n`r format (Sys.time(), format='%d-%b-%Y')`"

output: word_document
---
<!-- For different data format: -->
<!-- date: "`r format (Sys.time(), format='%d-%b-%Y')`"  : 13-Jan-2023 --> 
<!-- date: "`r format (Sys.time(), format='%Y-%m-%d')``" : 2023-01-13 -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE,comment=NA,results="asis")#results='asis'markup
library (haven);             # Imports and export SPSS (.sav) data
library (labelled);          # Calls value label, variable label and other information of the data
library (tidyverse);         # Managing data files with a better representation  
library (dplyr)              # Managing the functions using pipes %>%
library (sjlabelled)         # Supports 'rename_at', 'var_labels' and 'add_value_labels' functions
# library (Hmisc)
library(foreign)
library(car)
library(reshape2)
library(gmodels)
library(flextable)
# library('plyr')
library(epiDisplay)

source("./Lib/DPtool.R")

source("./Lib/linaconf.R")


```

## 1. Abstract

-   For data produced using a panel design, ADA applies the following additional deidentification process to decrease the risk of identification through linking responses across data using panel respondents.

-   The output produced below reports the k-anonymity (k=3) performed on the data, achieved by (a) classifying combinations of demographic variables with fewer than four responses as unique, and (b) recoding specific individual responses as missing to suppress each of those unique combinations. To limit the number of unique combinations to deal with, only four demographic variables will be retained in the data.

-   Restricted data handling: Any demographic variables removed in the above can be made available in a second data file with highly restricted access conditions. The full responses for the suppressed demographics will also be published in the restricted version.

## 2. Included demographics

Only four of the following demographic variables can be included in the general access data files:

-   Gender

-   Age

-   Education

-   State

-   Income

-   Country of birth

Additional demographic variables would require excessive aggregation or suppression. This syntax is designed to confidentialise four demographic variables only.

ADA will remove all other potentially identifying variables from the general release version of the data file, consistent with our standard risk assessment process. 

A more complete version of the data can be released as a RESTRICTED data file with access limited to specific users. Access conditions will be determined by ADA in consultation with the data owner(s).

## 3. Confidentialisation

How will panel data be confidentialised at ADA?

### a. First, age is categorized into seven categories, and gender is recoded to include only male and female (other categories are recoded as missing).

This is completed during the initial data cleaning process. Categories are collapsed to protect sensitive and low-frequency categories. The complete data will be available in the restricted version of the data.

Low-frequency categories are recoded as missing to ensure they cannot be identified. It is sometimes not sufficient to code those responses as 'other' or similar as they may still be unique enough as to be identifiable.

```{r}
# # Populate the section below with your project information:
- Enter the file path and original variable names (for gender, education, age, and state) in your data. Also include those variable names in the rmvar command.
- Replace the missing value codes with any values in your data that should be recoded as missing in the deidentified version (i.e., any low-frequency categories that might lead to re-identification of participants in that category).
- 

######################################################################
#################### Variable Name Specification #####################
######################################################################
#
# file_path <- ''                                              #destination to save confidentialised data
# 
# p_gender_name_ori <- ""                                      #gender variable name in the original data
# p_gender_name <- "p_gender_sdc"                              #gender variable name saving to the confidentialised data
# 
# p_age_group_name_ori <- ""                                   #age group variable name in the original data
# p_age_group_name <- "p_age_group_sdc"                        #age group variable name saving to the confidentialised data
# 
# p_education_name_ori <- ""                                   #education level variable name in the original data
# p_education_name <- "p_education_sdc"                        #education level variable name saving to the confidentialised data
#   
# p_state_name_ori <- ""                                       #state variable name in the original data
# p_state_name <- "p_state_sdc"                                #state variable name saving to the confidentialised data
# 
# missing_value_in_original <- c(-99:-1,90:99,NA)           #values (and value ranges) to be recoded as missing (e.g., N/A, sys missing, other, etc.)
# missing_value_in_original_gender <- c(-99:-1,90:99,NA,3)  #as above, but include any variable-specific values to recode as missing

# missing_value <- -9999                                    #code for all missing and confidentialised values in the confidentialised data
# missing_label <- 'Missing/Confidentialised'               #label for all missing and confidentialised values in the confidentialised data
# max_iteration <- 5                                        #maximum number of iterations to detect and suppress unique response combinations


# rm_var <- c(p_gender_name_ori,p_age_group_name_ori,p_education_name_ori,p_state_name_ori)       #variables removed from confidentialised data
# save_spss_filepath <- './.sav'   # Path(s) to save confidentialised data.
# save_csv_filepath <- './.csv'
# save_sas_filepath <- './.sas7bdat'
# save_dta_filepath <- './.dta'


######################################################################
######################### ANU POll Template ##########################
######################################################################
# 
# file_path <- 'Z:/assda/publish/ANU/Archivists/Weifan/ANUpoll data/ANUPoll 43 100007/02_ANUPoll_43_Data_File_100007.sav'
# 
# p_gender_name_ori <- 'gender_con'                            #gender variable name in the original data
# p_gender_name <- 'p_gender_sdc'                              #gender variable name saving to the confidentialised data
# 
# p_age_group_name_ori <- "p_ADA_age_group"                    #age group variable name in the original data
# p_age_group_name <- "p_age_group_sdc"                        #age group variable name saving to the confidentialised data
# 
# p_education_name_ori <- "d_education"                        #education level variable name in the original data
# p_education_name <- "p_education_sdc"                        #education level variable name saving to the confidentialised data
# 
# p_state_name_ori <- "p_state"                                #state variable name in the original data
# p_state_name <- "p_state_sdc"                                #state variable name saving to the confidentialised data
# 
# missing_value_in_original <- c(-99:-1,90:99,NA)           #recode values as missing
# missing_value_in_original_gender <- c(-99:-1,90:99,NA,3)  #also recode '3' as missing for gender
# missing_value_in_original_age <- missing_value_in_original
# missing_value_in_original_state <- missing_value_in_original
# missing_value <- -9999                                    #confidentialised value that save to the confidentialised data
# missing_label <- 'Missing/Confidentialised'               #confidentialised value name that save to the confidentialised data
# max_iteration <- 3                                        #the number of the iterations that do the k-anonymity
#
# rm_var <- c(p_gender_name_ori,p_age_group_name_ori,p_education_name_ori,p_state_name_ori) #remove original variables
#                                                           
# save_spss_filepath <- './2_ANUPoll_43_SPSS_100007.sav'    # Path(s) to save confidentialised data.
# save_csv_filepath <- './2_ANUPoll_43_CSV_100007.csv'
# save_sas_filepath <- ''
# save_dta_filepath <- ''


######################################################################
###################### Social Cohesion Template ######################
######################################################################
#
# file_path <- './Social_Cohesion_Survey_2021_SPSS_100075_RESTRICTED.sav'    
# 
# p_gender_name_ori <- 'dem2'                               #gender variable name in the original data
# p_gender_name <- 'p_gender_sdc'                           #gender variable name saving to the confidentialised data
# 
# p_age_group_name_ori <- "dem1a"                           #age group variable name in the original data
# p_age_group_name <- "p_age_group_sdc"                     #age group variable name saving to the confidentialised data
# 
# p_education_name_ori <- "dem10"                           #education level variable name in the original data
# p_education_name <- "p_education_sdc"                     #education level variable name saving to the confidentialised data
# 
# p_state_name_ori <- "state"                               #state variable name in the original data
# p_state_name <- "p_state_sdc"                             #state variable name saving to the confidentialised data
# 
# missing_value_in_original <- c(-99:-1,90:99,NA)               #recode values as missing
# missing_value_in_original_gender <- c(-99:-1,90:99,NA,3)      #also recode '3' as missing for gender
# missing_value_in_original_education <- c(-99:-1,90:99,NA,11)  #also recode '11' as missing for educatino
# missing_value_in_original_age <- missing_value_in_original
# missing_value_in_original_state <- missing_value_in_original
# 
# missing_value <- -9999                                    #code for all missing and confidentialised values in the confidentialised data
# missing_label <- 'Missing/Confidentialised'               #label for all missing and confidentialised values in the confidentialised data
# max_iteration <- 5                                        #maximum number of iterations to detect and suppress unique response combinations
#
# rm_var <- c(p_gender_name_ori,p_age_group_name_ori,p_education_name_ori,p_state_name_ori) #remove original variables
#  
# save_spss_filepath <- './2_Social_Cohesion_2021_SPSS_100075.sav'  # Path(s) to save confidentialised data.
# save_csv_filepath <- './2_Social_Cohesion_2021_CSV_100075.csv'
# save_sas_filepath <- ''
# save_dta_filepath <- ''


######################################################################
######################## Lowy Poll Template ##########################
######################################################################
#
# file_path <- ''                                              #destination to save confidentialised data
# 
# p_gender_name_ori <- ""                                      #gender variable name in the original data
# p_gender_name <- "p_gender_sdc"                              #gender variable name saving to the confidentialised data
# 
# p_age_group_name_ori <- ""                                   #age group variable name in the original data
# p_age_group_name <- "p_age_group_sdc"                        #age group variable name saving to the confidentialised data
# 
# p_education_name_ori <- ""                                   #education level variable name in the original data
# p_education_name <- "p_education_sdc"                        #education level variable name saving to the confidentialised data
#   
# p_state_name_ori <- ""                                       #state variable name in the original data
# p_state_name <- "p_state_sdc"                                #state variable name saving to the confidentialised data
# 
# missing_value_in_original <- c(-99:-1,90:99,NA)           #values (and value ranges) to be recoded as missing (e.g., N/A, sys missing, other, etc.)
# missing_value_in_original_gender <- c(-99:-1,90:99,NA,3)  #as above, but include any variable-specific values to recode as missing

# missing_value <- -9999                                    #code for all missing and confidentialised values in the confidentialised data
# missing_label <- 'Missing/Confidentialised'               #label for all missing and confidentialised values in the confidentialised data
# max_iteration <- 5                                        #maximum number of iterations to detect and suppress unique response combinations


# rm_var <- c(p_gender_name_ori,p_age_group_name_ori,p_education_name_ori,p_state_name_ori)       #variables removed from confidentialised data
# save_spss_filepath <- './.sav'   # Path(s) to save confidentialised data.
# save_csv_filepath <- './.csv'
# save_sas_filepath <- './.sas7bdat'
# save_dta_filepath <- './.dta'

```

```{r}

data <- haven::read_sav(file_path)

#Note 2. preprocessing may be required as well. For instance, group continuous age variable to categorical
#Note 4. usually state variable does not have NA values, then We add NA catagory to the State.

######################################################################
######## Grouping missing values together into one category ##########
######################################################################

data[[p_gender_name]] <- group_values(data[[p_gender_name_ori]],missing_value_in_original_gender,missing_value,missing_label)

data[[p_age_group_name]]<- group_values(data[[p_age_group_name_ori]],missing_value_in_original_age,missing_value,missing_label)

data[[p_education_name]]<- group_values(data[[p_education_name_ori]],missing_value_in_original_education,missing_value,missing_label)

data[[p_state_name]]<- group_values(data[[p_state_name_ori]],missing_value_in_original_state,missing_value,missing_label)


################################################################################
######## Include a missing code for variables that have no missing data ########
################################################################################

# May need new value label for unknown/refused [if there is no missing data at all].
# data <- add_new_value(data,p_state_name_ori,c('Refused'),c(missing_value))
```

### b.Frequency tables

```{r fig.align='center'}
cat('\n');cat('\n');cat('\n');cat('\n');
freqtab_g1 <- tab1(labelled::to_factor(data[[p_gender_name]]) ,graph = F)
freqtab_g1$first.line <- 'Frequency table for gender'
cat('\n');cat('\n') 
knitr::kable(freqtab_g1$output.table,caption = freqtab_g1$first.line,align = 'c') 

freqtab_e1 <- tab1(labelled::to_factor(data[[p_education_name]]) ,graph = F)
freqtab_e1$first.line <- 'Frequency table for education level'
cat('\n');cat('\n')
knitr::kable(freqtab_e1$output.table ,caption = freqtab_e1$first.line,align = 'c' )


freqtab_a1 <- tab1(labelled::to_factor(data[[p_age_group_name]]) ,graph = F)
freqtab_a1$first.line <- 'Frequency table for age group'
cat('\n');cat('\n')
knitr::kable(freqtab_a1$output.table ,caption=freqtab_a1$first.line,align = 'c')

freqtab_s1 <- tab1(labelled::to_factor(data[[p_state_name]]) ,graph = F)
freqtab_s1$first.line <- 'Frequency table for state'
cat('\n');cat('\n')
knitr::kable(freqtab_s1$output.table,caption = freqtab_s1$first.line,align = 'c')

# data.frame(freqtab1[2])
```

### c. Identify unique combinations of responses across the key demographic variables

First we replace missing values with an asterisk (*). We then concatenate responses across the four demographic variables to identify combinations of responses that are unique (i.e., shared by fewer than four respondents).* **Unique Combinations**\* of all four or any three demographics are flagged.

Missing data is coded as an asterisk for ease of identifying missing data in the summary tables.

```{r include=FALSE}
p_gender_string <- as.character(data[[p_gender_name]])
p_gender_string[which(p_gender_string==missing_value)] <- '*'

p_state_string <- as.character(data[[p_state_name]])
p_state_string[which(p_state_string==missing_value)] <- '*'

p_education_string<- as.character(data[[p_education_name]])
p_education_string[which(p_education_string==missing_value)] <- '*'

p_age_group2_string<- as.character(data[[p_age_group_name]])
p_age_group2_string[which(p_age_group2_string==missing_value)] <- '*'


ftable(table(labelled::to_factor(data[[p_gender_name]]),p_gender_string ))
cat('\n')
ftable(table( labelled::to_factor(data[[p_state_name]]),p_state_string))
ftable(table( labelled::to_factor(data[[p_education_name]]),p_education_string))
ftable(table( labelled::to_factor(data[[p_age_group_name]]),p_age_group2_string))

```

```{r include=FALSE}


data_occ <- subset(data,select =  c(p_gender_name,p_education_name,p_age_group_name,p_state_name))
data_occ$uniques4<- paste0(p_gender_string,p_education_string,p_age_group2_string,p_state_string)
data_occ_freq <- data_occ %>%  # coresponding to
  group_by(uniques4) %>%
  dplyr::summarize(count=n())
# data_occ_freq
number_occ_4 <- merge(data_occ,data_occ_freq,by =c('uniques4'))
occ_table <- tab1(number_occ_4$count,graph = FALSE);
occ_table$first.line <- "Frequency table for count of combinations: ***gender, education, age, state*** \n"
occ_table
cat('\n');cat('\n');
k3_4 <- rep(0,nrow(number_occ_4))
k3_4[which(number_occ_4$count<3)] <- 1
k3_4[which(number_occ_4[[p_gender_name]]==missing_value)] <- 0
k3_4[which(number_occ_4[[p_state_name]]==missing_value)] <- 0
k3_4[which(number_occ_4[[p_age_group_name]]==missing_value)] <- 0
k3_4[which(number_occ_4[[p_education_name]]==missing_value)] <- 0
ftable(k3_4)


cat("\n");cat("\n");cat("\n")
data_occ <- subset(data,select =  c(p_gender_name,p_education_name,p_age_group_name))
data_occ$uniques3a<- paste0(p_gender_string,p_education_string,p_age_group2_string)
data_occ_freq <- data_occ %>%  # coresponding to
  group_by(uniques3a) %>%
  dplyr::summarize(count=n())
number_occ_3a <- merge(data_occ,data_occ_freq,by =c('uniques3a') )
tab1(number_occ_3a$count,graph = FALSE);cat('\n');cat('\n')

k3_3a <- rep(0,nrow(number_occ_3a))
k3_3a[which(number_occ_3a$count<3)] <- 1

k3_3a[which(number_occ_3a[[p_gender_name]]==missing_value)] <- 0
k3_3a[which(number_occ_3a[[p_age_group_name]]==missing_value)] <- 0
k3_3a[which(number_occ_3a[[p_education_name]]==missing_value)] <- 0
ftable(k3_3a)
cat("\n");cat("\n");cat("\n")


data_occ <- subset(data,select =  c(p_gender_name,p_education_name,p_state_name))
data_occ$uniques3b<- paste0(p_gender_string,p_education_string,p_state_string)
data_occ_freq <- data_occ %>%  # coresponding to
  group_by(uniques3b) %>%
  dplyr::summarize(count=n())
# data_occ_freq
number_occ_3b <- merge(data_occ,data_occ_freq,by =c('uniques3b') )
tab1(number_occ_3b$count,graph = FALSE);cat('\n');cat('\n');
k3_3b <- rep(0,nrow(number_occ_3b))
k3_3b[which(number_occ_3b$count<3)] <- 1
k3_3b[which(number_occ_3b[[p_gender_name]]==missing_value)] <- 0
k3_3b[which(number_occ_3b[[p_state_name]]==missing_value)] <- 0
k3_3b[which(number_occ_3b[[p_education_name]]==missing_value)] <- 0
ftable(k3_3b)
cat("\n");cat("\n");cat("\n")


data_occ <- subset(data,select =  c(p_gender_name,p_age_group_name,p_state_name))
data_occ$uniques3c<- paste0(p_gender_string,p_age_group2_string,p_state_string)
data_occ_freq <- data_occ %>%  # corresponding to
  group_by(uniques3c) %>%
  dplyr::summarize(count=n())
# data_occ_freq
number_occ_3c <- merge(data_occ,data_occ_freq,by =c('uniques3c') )
tab1(number_occ_3c$count,graph = FALSE);cat('\n');cat('\n')

k3_3c <- rep(0,nrow(number_occ_3c))
k3_3c[which(number_occ_3c$count<3)] <- 1
k3_3c[which(number_occ_3c[[p_gender_name]]==missing_value)] <- 0
k3_3c[which(number_occ_3c[[p_state_name]]==missing_value)] <- 0
k3_3c[which(number_occ_3c[[p_age_group_name]]==missing_value)] <- 0
ftable(k3_3c)
cat("\n");cat("\n");cat("\n")

data_occ <- subset(data,select =  c(p_education_name,p_age_group_name,p_state_name))
data_occ$uniques3d<- paste0(p_education_string,p_age_group2_string,p_state_string)
data_occ_freq <- data_occ %>%  # coresponding to
  group_by(uniques3d) %>%
  dplyr::summarize(count=n())
# data_occ_freq
number_occ_3d <- merge(data_occ,data_occ_freq,by =c('uniques3d') )
tab1(number_occ_3d$count,graph = FALSE)
cat('\n')
k3_3d <- rep(0,nrow(number_occ_3d))
k3_3d[which(number_occ_3d$count<3)] <- 1
k3_3d[which(number_occ_3d[[p_education_name]]==missing_value)] <- 0
k3_3d[which(number_occ_3d[[p_state_name]]==missing_value)] <- 0
k3_3d[which(number_occ_3d[[p_age_group_name]]==missing_value)] <- 0
ftable(k3_3d)
cat("\n");cat("\n");cat("\n")
```

### d. Removing identification risk by suppressing demographic responses

Unique combinations are suppressed by replacing one response in each unique combination of responses with missing data (i.e., an asterisk).
The algorithm will suppress a given demographic value if the combination of the other three demographics is more frequent that any other combination of three. For example, a respondent’s education response will be suppressed if their gender/age/state combination appears more often in the data relative to other combinations of their demographics (gender/education/state, gender/education/age, education/age/state). In this example, the education response carries the greatest risk of identification so is selected for suppression. In this example, gender/age/state is a commonly occurring combination, therefore education is the outlier, or the most unique of the four demographics for that respondent. Therefore, education carries the greatest risk of identification so is selected for suppression.

We repeat this process iteratively until no additional unique combinations are detected.

```{r results='markup'}
data_con <- data
for (i in 1:max_iteration) {
  cat('#### the ',i,' iteration starts: \n')
  results <- conf_LinA_short(data_con,p_gender_name,p_age_group_name,p_education_name,p_state_name,NA_value=missing_value)
  data_con <- results$data_con
  if (!results$flag) {#if no need for iterations
    cat('\n\n #### ')
    cat('The confidentiality process was completed in  ',i-1,' of iterations ####')
    break
  }
  cat('\n')
}
```

## 3. Results and Comparison

In this section, we compare the frequency of responses for each variable before and after suppression so users can examine the distribution of missing data.

Frequency tables report the number of responses in each response category before and after suppression. For each demographic variable, table 3.X.1  below reports exact combinations of responses that are unique (i.e., fewer than 3). And table 3.X.2 confirms that those unique combinations were suppressed by recoding one demographic response as missing.

### 3.1. Gender

***Table 3.1.1 Every combination of responses and the number (count) of each where the response for Gender will be replaced with missing data.***

```{r}
flexPrintFun <- function(x){                        #Function that print table with 2 columns
  flextable(x) %>%
    width(j=1, width = 1.00) %>%
    width(j=1, width = 1.00) %>%
    width(j=1, width = 1.00) %>%
    width(j=1, width = 1.00) %>%
    width(j=1, width = 1.00) %>%
    hrule(rule="auto", part="all") %>%
    fontsize(part="header", size=8) %>%
    fontsize(part="body", size=8) 
}



list1 <- data[[p_gender_name]]
list2 <- data_con[[p_gender_name]]
posi <- which((list1 == list2)==FALSE )

data_t <-  data[posi,][c(p_gender_name,p_education_name,p_age_group_name,p_state_name)]
# data_t <-  data_string[posi,][c(p_gender_string,p_education_string,p_age_group2_string,p_state_string)]


names(data_t) <- c('p_gender_name','p_education_name','p_age_group_name','p_state_name')

freq_t <- data_t %>% group_by(p_gender_name,p_education_name,p_age_group_name,p_state_name) %>% summarise(count=n()) %>% as.data.frame() %>% mutate_all(as.character)
names(freq_t) <- c('gender','education','age','state','count')
freq_t[freq_t==missing_value]='*'
# cat('there are total ',sum(freq_t$count),' of gender has been suppressed.')
theme_box(flexPrintFun(freq_t ))
cat("\n");cat("\n");cat("\n");
```

***Table 3.1.2: Frequency table for Gender before and after suppression***

```{r echo=FALSE,results="markup"}
# flexPrintFun <- function(x){                        #Function that prints table with 2 columns
#   flextable(x) %>%
#     width(j=1, width = 3.00) %>%
#     width(j=2, width = 1.00) %>%
#     width(j=3, width = 1.00) %>%
#     width(j=3, width = 1.00) %>%
#     hrule(rule="auto", part="all") %>%
#     fontsize(part="header", size=8) %>%
#     fontsize(part="body", size=8) 
# }


freqtab_g2 <- tab1(labelled::to_factor(data_con[[p_gender_name]]) ,graph = F)
# rname <- c( paste(names(attributes( data_con[[p_gender_name]])$labels),attributes( data_con[[p_gender_name]])$labels,sep =  ': '), "total")
# rname <- rownames( freqtab_g2$output.table)
# rname <- c(attributes( data_con[[p_gender_name]])$labels )
# ,names(attributes( data_con[[p_gender_name]])$labels)

value <- c(unname(attributes( data_con[[p_gender_name]])$labels),'')
value_label <-c( names(attributes( data_con[[p_gender_name]])$labels),'total')
freq_con <- data.frame(cbind(value,value_label,data.frame(freqtab_g1$output.table)$Frequency,data.frame(freqtab_g2$output.table)$Frequency ,data.frame(freqtab_g2$output.table)$Frequency-data.frame(freqtab_g1$output.table)$Frequency))
colnames(freq_con) <- c('Value', 'Value Label','#before','#after',"Difference")


# rownames(freq_con) <- rname

knitr::kable(freq_con,caption = "",align = 'c')
```


```{r echo=FALSE}


cat('\n ')

if (as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])==1){
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])," gender response (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))
}else{
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])," gender responses (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")  
}

cat('\n')

```

### 3.2. Education

***Table 3.2.1: Every combination of k\<3 demographic responses and the number (count) of each combination, and setting these Education to missing value.***

```{r}
list1 <- data[[p_education_name]]
list2 <- data_con[[p_education_name]]
posi <- which((list1 == list2)==FALSE )

data_t <-  data[posi,][c(p_gender_name,p_education_name,p_age_group_name,p_state_name)]
names(data_t) <- c('p_gender_name','p_education_name','p_age_group_name','p_state_name')

freq_t <- data_t %>% group_by(p_gender_name,p_education_name,p_age_group_name,p_state_name) %>% summarise(count=n())%>% as.data.frame() %>% mutate_all(as.character)
names(freq_t) <- c('gender','education','age','state','count')
freq_t[freq_t==missing_value]='*'
theme_box(flexPrintFun(freq_t ))
```

***Table 3.2.1: Frequency table shows education before and after suppression***

```{r echo=FALSE}
freqtab_e2 <- tab1(labelled::to_factor(data_con[[p_education_name]]) ,graph = F)
# rname <- c( paste(names(attributes( data_con[[p_education_name]])$labels),attributes( data_con[[p_education_name]])$labels,sep =  ': '), "total")
# freq_con <- data.frame(cbind(rname,data.frame(freqtab_e1$output.table)$Frequency,data.frame(freqtab_e2$output.table)$Frequency ,data.frame(freqtab_e2$output.table)$Frequency-data.frame(freqtab_e1$output.table)$Frequency))
# colnames(freq_con) <- c('value label','Frequency before','After',"diff")
# cat("*Table 2: Frequency table shows education before and after suppression*")
# theme_box(flexPrintFun(freq_con ))

value <- c(unname(attributes( data_con[[p_education_name]])$labels),'')
value_label <-c( names(attributes( data_con[[p_education_name]])$labels),'total')
freq_con <- data.frame(cbind(value,value_label,data.frame(freqtab_e1$output.table)$Frequency,data.frame(freqtab_e2$output.table)$Frequency ,data.frame(freqtab_e2$output.table)$Frequency-data.frame(freqtab_e1$output.table)$Frequency))
colnames(freq_con) <- c('Value', 'Value Label','#before','#after',"Difference")

knitr::kable(freq_con,caption = "")
```


```{r echo=FALSE}
cat('\n')
if (as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])==1){
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])," education response (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))


}else{
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])," education responses (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))

}

cat('\n')

```

### 3.3. Age group

***Table 3.3.1: Every combination of k\<3 demographic responses and the number (count) of each combination, and setting these Age group to missing value.***

```{r}
list1 <- data[[p_age_group_name]]
list2 <- data_con[[p_age_group_name]]
posi <- which((list1 == list2)==FALSE )

data_t <-  data[posi,][c(p_gender_name,p_education_name,p_age_group_name,p_state_name)]
names(data_t) <- c('p_gender_name','p_education_name','p_age_group_name','p_state_name')

freq_t <- data_t %>% group_by(p_gender_name,p_education_name,p_age_group_name,p_state_name) %>% summarise(count=n())%>% as.data.frame() %>% mutate_all(as.character)
names(freq_t) <- c('gender','education','age','state','count')
freq_t[freq_t==missing_value]='*'
theme_box(flexPrintFun(freq_t ))
```

***Table 3.3.2: Frequency table shows age group before and after suppression***

```{r echo=FALSE}
freqtab_a2 <- tab1(labelled::to_factor(data_con[[p_age_group_name]]) ,graph = F)
# rname <- c( paste(names(attributes( data_con[[p_age_group_name]])$labels),attributes( data_con[[p_age_group_name]])$labels,sep =  ': '), "total")
# freq_con <- data.frame(cbind(rname,data.frame(freqtab_a1$output.table)$Frequency,data.frame(freqtab_a2$output.table)$Frequency ,data.frame(freqtab_a2$output.table)$Frequency-data.frame(freqtab_a1$output.table)$Frequency))
# colnames(freq_con) <- c('value label','Frequency before','After',"diff")
# cat("*Table 2: Frequency table shows age group before and after suppression*")
# theme_box(flexPrintFun(freq_con ))

value <- c(unname(attributes( data_con[[p_age_group_name]])$labels),'')
value_label <-c( names(attributes( data_con[[p_age_group_name]])$labels),'total')
freq_con <- data.frame(cbind(value,value_label,data.frame(freqtab_a1$output.table)$Frequency,data.frame(freqtab_a2$output.table)$Frequency ,data.frame(freqtab_a2$output.table)$Frequency-data.frame(freqtab_a1$output.table)$Frequency))
colnames(freq_con) <- c('Value', 'Value Label','#before','#after',"Difference")



knitr::kable(freq_con,caption = "",align = 'c')
```


```{r echo=FALSE}
cat('\n ')

if (as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])==1){
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)]),"age group response (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))
}else{
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)]),"age group responses (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))

}
cat('\n')
```

### 3.4. State

***Table 3.4.1: Every combination of k\<3 demographic responses and the number (count) of each combination, and setting these State to missing value.***

```{r}
list1 <- data[[p_state_name]]
list2 <- data_con[[p_state_name]]
posi <- which((list1 == list2)==FALSE )

data_t <-  data[posi,][c(p_gender_name,p_education_name,p_age_group_name,p_state_name)]
names(data_t) <- c('p_gender_name','p_education_name','p_age_group_name','p_state_name')

freq_t <- data_t %>% group_by(p_gender_name,p_education_name,p_age_group_name,p_state_name) %>% summarise(count=n())%>% as.data.frame() %>% mutate_all(as.character)
names(freq_t) <- c('gender','education','age','state','count')
freq_t[freq_t==missing_value]='*'
theme_box(flexPrintFun(freq_t ))

```

***Table 3.4.1: Frequency table shows state before and after suppression***

```{r echo=FALSE}
# cat("\n"); cat("\n");
freqtab_s2 <- tab1(labelled::to_factor(data_con[[p_state_name]]) ,graph = F)
# rname <- c( paste(names(attributes( data_con[[p_state_name]])$labels),attributes( data_con[[p_state_name]])$labels,sep =  ': '), "total")
# freq_con <- data.frame(cbind(rname,data.frame(freqtab_s1$output.table)$Frequency,data.frame(freqtab_s2$output.table)$Frequency ,data.frame(freqtab_s2$output.table)$Frequency-data.frame(freqtab_s1$output.table)$Frequency))
# colnames(freq_con) <- c('value label','Frequency before','After',"diff")
# cat("**")
# theme_box(flexPrintFun(freq_con ))
value <- c(unname(attributes( data_con[[p_state_name]])$labels),'')
value_label <-c( names(attributes( data_con[[p_state_name]])$labels),'total')
freq_con <- data.frame(cbind(value,value_label,data.frame(freqtab_s1$output.table)$Frequency,data.frame(freqtab_s2$output.table)$Frequency ,data.frame(freqtab_s2$output.table)$Frequency-data.frame(freqtab_s1$output.table)$Frequency))
colnames(freq_con) <- c('Value', 'Value Label','#before','#after',"Difference")




knitr::kable(freq_con,caption = "",align = 'c')
```


```{r echo=FALSE}
cat('\n ')
if (as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])==1){
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)]),"state response (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")
# theme_box(flexPrintFun(freq_con ))


}else{
  
  cat("In sum, ",as.integer(freq_con$Difference[which(freq_con$Value==missing_value)]),"state responses (",round(as.integer(freq_con$Difference[which(freq_con$Value==missing_value)])*100/as.integer(freq_con[['#before']][nrow(freq_con)]),3),"%) were replaced with missing data to remove unique combinations of demographic variables.")

}


cat('\n')
```

## 4. Export de-identified data files for general release

De-identified data files (with suppressed demographic data as described above) will be exported and saved to the current working directory for distribution on ADA Dataverse.

NB. The Australian Data Archive

```{r}

data_con_save <- data_con[ , -which(names(data_con) %in% rm_var )]

#####################################################################################################################
#######################   Write data in SPSS (.sav): Archivist may change the name and location #####################
######################################  ###############################################################################

if (!save_spss_filepath==''){
  write_spss(data_con_save, save_spss_filepath,drop.na = FALSE)
}

if (!save_dta_filepath==''){
  write_dta(data_con_save, save_dta_filepath,drop.na = FALSE,version = 14)
}
if (!save_csv_filepath==''){
  write_csv(data_con_save, save_csv_filepath)
}
if (!save_sas_filepath==''){
  write_sas(data_con_save, save_sas_filepath)
}


```
